---
title: "A UN Report on the Relationship between GDP and CO2 emission"
author: "Joohee Kim"
date: "1/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
library(tidyverse) # contains ggplot package
```

This report was prepared to the attention of the United Nations. It analyzes the relationship between a country's GDP, its life expectancy and CO2 emissions. Our goal is to determine to what degree a country’s economic strength or weakness may be related to its public health status and impact on climate pollution. We hypothesize that both life expectancy and CO2 emissions increase with a country's GDP.

```{r data}
gapminder_1997 <- read_csv("../data/gapminder_1997.csv")
View(gapminder_1997)
```

```{r gdp_lifeexp_1997}
ggplot(data = gapminder_1997) +
  aes(x = gdpPercap, y = lifeExp, color = continent) +
  labs(x = "GDP Per Capita", y = "Life Expectancy", title = "GDP per capita vs. Life Expectancy in 1997") +
  geom_point()
```